manuscript

### 2022-05-20 manuscript.Rmd
testing

---
title: "manuscript"
author: "Federico Segala, Aurelio Bruno, Alex Wade, Daniel Baker"
date: "`r Sys.Date()`"
output: html_document
---

@@

### Experiment 1

I'd suggest the following figures:

>>>>

---
title: "manuscript"
author: "Federico Segala, Aurelio Bruno, Alex Wade, Daniel Baker"
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

@@

### Experiment 1
nonsense
I'd suggest the following figures:
